Tabular Constraint Learning

### 2016-05-09 Paper/ECAI/tabular.tex
reworked the problem statement

@@

While the traditional CSP problem is given a set of variables and a set of constraints, and the task is to find an assignment, the {\bf inverse CSP} or the {\bf Tabular Constraint Learning Problem} can be defined as follows.\\
\\
{\bf Given }
\begin{itemize}
\item
a set of instantiated tables (so all cells have values) ${\cal T}$;
\item
a set of {\template}s ${\cal C}$;
\item
a set of groups ${\cal G}$ for the tables ${\cal T}$;
\end{itemize}
\noindent
{\bf Find}  the set of all constraints $s(G_1', ..., G_n')$ that 1) are satisfied  in ${\cal T}$, 2)
for which all $G_i' \subseteq G_i \in {\cal G}$ and  3) the groups $G_1', ... , G_n'$ satisfy the signature of the constraint template~$s \in {\cal C}$.

For instance, Figure 3 contains the solution to the tabular constraint learning problem
that uses the tables of Figure 1, the signatures of Table 1 and the set of groups mentioned in (\samuel{show groups somewhere}).

@@

\samuel{Not reworked yet from here ---}

@@

\tias{Redundancy instead of dependency}

  In theory each constraint is independent and equally useful. In practice, however, things are different. Assume that for some $g_x$ both \textit{series($g_x$)} and \textit{alldifferent($g_x$)} hold. From a user's perspective the last solution is useless, since he or she already knows that the series constraint implies the alldifferent constraint. To capture this condensed representation \cite{condensed} of solutions, we have introduced a specificity (generality) order between constraints, which is depicted using solid (dashed) arrows in Figure \ref{fig:learning_order}. This matters from implementation perspective as well, if we discovered that $g_x$ is not a permutation, then $g_x$ should not be tested for the series constraint at all. A solid lines from $t_1$ to $t_2$ indicates that $t_2$ is \textit{more specific} than $t_1$ and if $C_1=t_1^S$ from $t_1$ does not hold, then the constraint $C_2=t_2^S$ from $t_2$ does not hold neither. A dashed arrow from $t_1$ to $t_2$ indicates that $t_1$ is \textit{a more specific} constraint than $t_2$ and therefore if $C=t_1^S$ from $t_1$ holds it should not be tested for $t_2$.

Let $t$ be a \template, $S$ be a mapping from variables to the subgroups of \groups, \dependencies be the DAG of constraint specificity, then the constraint $C$ equal to $t^S$ is called \textit{the most specific} wrt \dependencies iff $C$ holds and there is no other template $t_{*}$ for which the constraint $C_{*}=t_{*}^S$ holds and $t_{*}$ is more specific in \dependencies.

Let us introduce the version of tabular constraint learning that takes into account the specificity relation between constraints.

\begin{minipage}[c]{14em}
  \vspace{5pt}
  \begin{tabular}{ll}
    \multicolumn{2}{l}{{\textbf{Condensed Tabular Constraint Learning Problem}}}\\
    \vspace{-4pt}
    &\\
    \textbf{Given:}& the set of all groups $\groups$ and of \template's $\constraints$,\\
    & a constraint specificity DAG \dependencies \\
    \textbf{Find:}& all the most specific wrt \dependencies constraints $C$ over \groups\\
    & for each $t$ in \constraints \\
  \end{tabular}
  \vspace{6pt}
\end{minipage}

@@

@@

\subsubsection{Generality ordering}

>>>>

\usepackage{amsthm}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

@@

While the traditional CSP problem is given a set of variables and a set of constraints, and the task is to find an assignment, the {\bf inverse CSP} or the {\bf Tabular Constraint Learning Problem} can be defined as follows.\\
\begin{definition}[Tabular Constraint Learning]\label{def:problem_statement}
  Let ${\cal T}$ a set of instantiated tables (all cells have values),  ${\cal C}$ be a set of {\template}s, ${\cal G}$ be a set of groups  for the tables ${\cal T}$, then find the set of all constraints $s(G_1', ..., G_n')$ that are satisfied  in ${\cal T}$, for which all $G_i' \subseteq G_i \in {\cal G}$, and the groups $G_1', ... , G_n'$ satisfy the signature of the constraint template~$s \in {\cal C}$.
\end{definition}
% {\bf Given }
% \begin{enumerate}
% \item
% a set of instantiated tables (so all cells have values) ${\cal T}$;
% \item
% a set of {\template}s ${\cal C}$;
% \item
% a set of groups ${\cal G}$ for the tables ${\cal T}$;
% \end{enumerate}
% \noindent
% {\bf Find}  the set of all constraints $s(G_1', ..., G_n')$ that 
% \begin{enumerate}
% \item are satisfied  in ${\cal T}$;
% \item for which all $G_i' \subseteq G_i \in {\cal G}$ ;
% \item the groups $G_1', ... , G_n'$ satisfy the signature of the constraint template~$s \in {\cal C}$.
% \end{enumerate}
For instance, Figure 3 contains the solution to the tabular constraint learning problem
that uses the tables of Figure 1, the signatures of Table 1 and the set of groups mentioned in (\samuel{show groups somewhere}).

@@

@@

In theory each constraint is independent and equally useful. In practice, however, things are different and some constraints are considered to be \textit{redundant}. Assume that for some $g_x$ both \textit{series($g_x$)} and \textit{alldifferent($g_x$)} hold. From a user's perspective the last solution is useless, since he or she already knows that the series constraint implies the alldifferent constraint, or formally speaking $\forall g_x{:}~\textit{series}(g_x) \rightarrow \textit{alldifferent}(g_x)$  holds. To capture this condensed representation \cite{condensed} of solutions, we have introduced a specificity order between constraints, which is depicted using solid arrows in Figure \ref{fig:learning_order}. This matters from implementation perspective as well, if we discovered that $g_x$ is not a permutation, then $g_x$ should not be tested for the series constraint at all.

Formally, we say that a constraint template $t_1$ is \textit{more specific} than a constraint template $t_2$ iff for $t_1$ and $t_2$  holds the statements of the form: $\forall g_1, \dots, g_n{:}~ t_1(g_1,\dots,g_n) \rightarrow t_2(g_h, \dots, g_k)$ where $1 \leq h \leq k \leq n$. The intuition behind the formula is the following, if a list of groups is a solution for $t_1$ then its subset is also a solution for $t_2$.

Let us introduce the version of tabular constraint learning by modifying Definition \ref{def:problem_statement} that takes into account the specificity relation between constraint templates.

\begin{definition}[Condensed Tabular Constraint Learning]\label{def:condensed_problem_statement}
  Let ${\cal T}$ a set of instantiated tables (all cells have values),  ${\cal C}$ be a set of {\template}s,  ${\cal G}$ be a set of groups for the tables ${\cal T}$, \dependencies be the set of all specifity rules, then find the set of all constraints $s(G_1', ..., G_n')$ that are satisfied  in ${\cal T}$, for which all $G_i' \subseteq G_i \in {\cal G}$, the groups $G_1', ... , G_n'$ satisfy the signature of the constraint template~$s \in {\cal C}$ and there is no $s'$ in ${\cal C}$ such that $s'(G_h',\dots,G_k')$ holds (for $1 \leq h \leq k \leq n$) and  $s'$ is more specific than $s$ in \dependencies.
\end{definition}

% \begin{minipage}[c]{14em}
%   \vspace{5pt}
%   \begin{tabular}{ll}
%     \multicolumn{2}{l}{{\textbf{Condensed Tabular Constraint Learning Problem}}}\\
%     \vspace{-4pt}
%     &\\
%     \textbf{Given:}& the set of all groups $\groups$ and of \template's $\constraints$,\\
%     & a constraint specificity DAG \dependencies \\
%     \textbf{Find:}& all the most specific wrt \dependencies constraints $C$ over \groups\\
%     & for each $t$ in \constraints \\
%   \end{tabular}
%   \vspace{6pt}
% \end{minipage}

@@

\sergey{still need to remove some repetitions later on about specisifity}

@@

\subsubsection{Generality ordering}
\sergey{should we show all the formulas here? or some maybe and say that the specificity DAG can be extracted?}
